% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{report}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Berlin AirBnB DL nice title},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=4cm, right=3cm, top=2.5cm, bottom=2.5cm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage[english]{babel}
\usepackage{amsmath, bm}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Berlin AirBnB DL nice title}
\author{}
\date{\vspace{-2.5em}15 Januar 2022}

\begin{document}
\maketitle

\begin{titlepage}
\vspace*{3.5cm}
\centering
{\LARGE DL}\\[2\baselineskip]
\selectlanguage{english}
{\LARGE  Term Paper  \\
 Submitted in partial fulfillment of the requirements for the  master's seminar\\
\textquotedblleft Advanced Statistical Programming \textquotedblright\ \\
of the \\
Faculty the Economic Sciences \\
of the \\
Georg August University of Göttingen\\
2022 \par}
\vspace*{\fill}
\begin{flushleft}
Juan Sebastián Aristizábal Ortiz\\
Tobias Rinnert

Date of submission: 06.03.2022\\
\vspace{10mm}
Advisor: Prof. Dr. Thomas Kneib\\
Center for Statistics\\
\end{flushleft}
\thispagestyle{empty}
\end{titlepage}

\hypertarget{abstract}{%
\chapter{Abstract}\label{abstract}}

This paper rocks because we rock.

Keywords: AI, such smart terms, many gradient descent, wow location and
scale.

\hypertarget{introduction-define-a-problem.}{%
\chapter{1. Introduction/ Define a
problem.}\label{introduction-define-a-problem.}}

Example cite. Tobi likes Francois Chollet and Allaire (2018).

\hypertarget{choose-a-measure-of-success-accuracy-precision}{%
\chapter{2. Choose a measure of success (accuracy?
Precision)}\label{choose-a-measure-of-success-accuracy-precision}}

\hypertarget{decide-how-to-evaluate-cross-validation}{%
\chapter{3. Decide how to evaluate (Cross
validation)}\label{decide-how-to-evaluate-cross-validation}}

\hypertarget{prepare-the-data-formatting-feature-engineering}{%
\chapter{4. Prepare the data (Formatting/ Feature
Engineering)}\label{prepare-the-data-formatting-feature-engineering}}

\hypertarget{develope-a-model-that-performs-better-tha-the-baseline}{%
\chapter{5. Develope a model that performs better tha the
baseline}\label{develope-a-model-that-performs-better-tha-the-baseline}}

\hypertarget{scale-up-and-develope-a-model-that-overfits.}{%
\chapter{6. Scale up and develope a model that
overfits.}\label{scale-up-and-develope-a-model-that-overfits.}}

\hypertarget{regularize-the-model-and-tune-hyperparameters.}{%
\chapter{7. Regularize the model and tune
hyperparameters.}\label{regularize-the-model-and-tune-hyperparameters.}}

\hypertarget{references}{%
\chapter{8. References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Chollet.2018}{}}%
Chollet, François, and J. J. Allaire. 2018. \emph{Deep Learning with r}.
Shelter Island: {Manning Publications}.

\end{CSLReferences}

\hypertarget{appendix}{%
\chapter{9. Appendix}\label{appendix}}

Example:

The conditional porbability density function of a gaussian response is

\begin{equation}
 \begin{gathered}
  f\left( y_i|\bm{x_i} \right) = \frac{1}{\sigma_i \sqrt{2\pi}} \exp \Bigg\{ { -\frac{1}{2} \left(\frac{y_i - \mu_i}{\sigma_i} \right)^2} \Bigg\} \\
 \end{gathered}
\end{equation}

T

\end{document}
