---
title: "Basic EDA"
author: "Sebastian"
date: "10 Januar 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
```

```{r}
listings <- read_csv("data/listings.csv")
reviews <- read_csv("data/reviews.csv")
neighbourhoods <- read_csv("data/neighbourhoods.csv")
grand_listings <- read_csv("data/listings.csv.gz")
grand_reviews <- read_csv("data/reviews.csv.gz")
calendar <- read_csv("data/calendar.csv.gz")

#grand_neighbourhoods <- read_csv("data/listings.csv.gz")
# View(listings)
# View(reviews)
# View(neighbourhoods)
```

3 Datasets. 
Main dataset: Listings. 
following variables and summary statistics:
```{r}
variable.names(listings)
#summary(listings)
```

```{r}
variable.names(grand_listings)
```

```{r}
variable.names(reviews)
```
```{r}
variable.names(grand_reviews)
```

```{r}
variable.names(neighbourhoods)
```

```{r}
variable.names(calendar)
```




Ideas for variable analysis:
- Language of name (EN vs DE).
- 

```{r}
model_small <- lm(price ~ ., data = listings)

```

```{r}
summary(model_small)
```

To Do:
- Identify metric scaled variables. 
- Sort the dataset to get metric variables suitible for a regression first. 
- Clean missing values. (Consider Nicos code). 
- Consider uniting all datasets in one. Or metric dataset and one categorical. 
- Text seems omnipresent. We need to use it. 
- What about the dataset we get for testing our model? How can it work if it isn't cleaned?

Correlation

```{r}
C <- cor(data)
symnum(C, cutpoints = c(0.3, 0.7, 0.8, 0.9, 0.95), corr = T)

heatmap(C)

data$id
data[,"id"]

# sapply(data, function(x) mean(x))

```


